---

output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

Draft data:

```{r}
draft <- as_tibble(read.csv("draft.csv"))
draft <- draft %>%
  select(!Phase) %>%
  rename(Number = `X.`,
         DraftedBy = `Drafted.By`,
         PlayerName = `Player.Name`,
         DraftedFrom = `Drafted.From`) %>%
  mutate(Rd = factor(Rd),
         DraftedBy = factor(DraftedBy),
         POS = factor(POS),
         DraftedFrom = factor(DraftedFrom))
head(draft, n = 3)
```

Lahman data - Info of players in the Major Leagues
```{r, echo = FALSE}
lehman <- as_tibble(read.csv("People.txt"))

lehman <- lehman %>%
  mutate(playerName = paste(nameFirst, nameLast),
         debut = as.Date(debut),
         finalGame = as.Date(finalGame),
         bats = factor(bats),
         throws = factor(throws)) %>%
  select(playerName, playerID, bats, throws, debut, finalGame) %>%
  filter(debut >= "2007-01-01")

joined.data <- left_join(draft, lehman, by = c("PlayerName" = "playerName"))
joined.data <- joined.data %>%
  mutate(major_league_player = ifelse(is.na(debut),  "No", "Yes")) %>%
  mutate(major_league_player = factor(major_league_player)) %>%
  select(PlayerName, debut, major_league_player, POS)

head(joined.data, n = 3)
```
# Add a column to determine if the draftee has made it to the majors


nonpitchers <- joined.data %>%
  filter(!POS  %in% c("P", "LHP", "RHP")) %>%
  select(PlayerName, playerID, Rd, Number, throws, bats, POS, debut, major_league_player)

minors_batting <- distinct(as_tibble(read.csv("batting.csv")), Name, .keep_all = TRUE)

joined.hitters <- left_join(nonpitchers, minors_batting, by = c("PlayerName" = "Name"))

complete <- joined.hitters%>%
  filter(!is.na(AB), AB != 0)%>%
  select(!c(Rk, min_playerid, teams, season, Pos.Summary, Lev, Tm, Age, playerID, Rd, Number, debut, throws, bats))

advanced_stats<- complete %>%
  filter(AB >= 20) %>%
  mutate(StrikePercentage = round(SO / AB, 4),
         ISO = SLG - BA,
         wOBA = ((.69*(BB-IBB)) + (.719*HBP) + (.87*(H - X2B - X3B - HR)) + (1.217*X2B) + (1.529*X3B) + (1.94*HR)) / (AB + BB - IBB + SF + HBP)) %>%
  select(c(PlayerName, major_league_player, POS, ISO, BA, wOBA, StrikePercentage))```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
